% !TeX root = cv_main.tex

\section*{\itshape Michael R. May}

\begin{adjustwidth}{1em}{}
Department of Integrative Biology, University of California, Berkeley\\
University Herbarium, University of California, Berkeley\\
Center for Population Biology, University of California, Davis\\

3040 Valley Life Sciences Building \#3140\\
Berkeley, CA 94720-3140\\
Email: \href{href:mikeryanmay@gmail.com}{\myuline{mikeryanmay@gmail.com}}\\
Website: \href{https://mikeryanmay.github.io/}{\myuline{mikeryanmay.github.io}}
\end{adjustwidth}

\subsection*{Education and Appointments}

\begin{tabularx}{\textwidth}{@{\hspace{1em}}lX}
    2020--present & Postdoctoral scholar, UC Davis\\
    2019--present & Postdoctoral scholar, UC Berkeley\\
    2011--2019    & PhD, Population Biology, UC Davis\\
    2008--2010    & BS, Evolution, Ecology and Biodiversity, UC Davis (Highest Honors)
\end{tabularx}

\subsection*{Publications}

\begin{etaremune}[topsep=0pt,itemsep=1.2em,partopsep=0pt,parsep=0pt]
    \item \textbf{May, M. R.} \& Rothfels, C. J. (2021). \textit{Mistreating birth-death models as priors in phylogenetic analysis compromises our ability to compare models.} \myuline{bioRxiv}. \href{https://www.biorxiv.org/content/10.1101/2021.07.12.452074v1}{DOI}. \href{https://www.youtube.com/watch?v=SWldXeWet68&feature=youtu.be}{Slides}.
    \item Tribble, C. M., Freyman, W. A., Landis, M. J., Lim, J. Y., Barido-Sottani, J., Kopperud, B. T., Höhna, S. \& \textbf{May, M. R.} (2021). \textit{RevGadgets: an R Package for visualizing Bayesian phylogenetic analyses from RevBayes.} \myuline{bioRxiv}. \href{https://www.biorxiv.org/content/10.1101/2021.05.10.443470v1}{DOI}.
    \item Höhna, S., Freyman, W. A., Nolen, Z., Huelsenbeck, J. P., \textbf{May, M. R.}, \& Moore, B. R. (2021). \textit{A Bayesian approach for estimating branch-specific speciation and extinction rates.} \myuline{bioRxiv}. \href{https://www.biorxiv.org/content/10.1101/2021.07.12.452074v1}{DOI}.
    \item Gao, J., \textbf{May, M. R.}, Rannala, B. \& Moore, B. R. (2021). \textit{Phylodynamic insights on the early spread of the COVID-19 pandemic and the efficacy of intervention measures.} \myuline{bioRxiv}. \href{https://www.biorxiv.org/content/10.1101/2021.05.01.442286v1}{DOI}.
    \item Barido-Sottani, J., Justison, J. A., Borges, Rui., Brown, J. M., Dismukes, W., do Rosario, P., ..., \textbf{May, M. R.} \& Heath, T. A. (2021). \textit{Lessons learned from organizing and teaching virtual phylogenetics workshops.} \myuline{In review.}
    \item \textbf{May, M. R.}, Contreras, D. L., Sundue, M. A., Nagalingum, N. S., Looy, C. V., \& Rothfels, C. J. (2021). \textit{Inferring the total-evidence timescale of Marattialean fern evolution in the face of model sensitivity.} \myuline{Systematic Biology}, in press. \href{https://doi.org/10.1093/sysbio/syab020}{DOI}. \href{https://www.youtube.com/watch?v=5H_u9bjn064}{Slides}.
    \item Thompson A., \textbf{May M. R.}, Moore, B. R. \& Kopp A. (2020). \textit{A hierarchical Bayesian mixture model for inferring the expression state of genes in transcriptomes.} \myuline{Proceedings of the National Academy of Sciences} 117(32), 19339–19346. \href{https://doi.org/10.1073/pnas.1919748117}{DOI}.
    \item \textbf{May, M. R.} \& Moore, B. R. (2020). \textit{A Bayesian approach for inferring the impact of a discrete character on rates of continuous-character evolution in the presence of background-rate variation.} \myuline{Systematic Biology} 69(3), 530–544. \href{https://doi.org/10.1093/sysbio/syz069}{DOI}.
    \item Turelli, M., Cooper, B. S., Richardson, K. M., Ginsberg, P. S., Peckenpaugh, B., Antelope, C. X., ..., \textbf{May, M. R.}, ... \& Hoffmann, A. A. (2018). \textit{Rapid global spread of wRi-like Wolbachia across multiple Drosophila.} \myuline{Current Biology} 28(6), 963–971. \href{https://linkinghub.elsevier.com/retrieve/pii/S0960982218301696}{DOI}.
    \item Jiao, Y., Peluso, P., Shi, J., Liang, T., Stitzer, M. C., Wang, B., ..., \textbf{May, M. R.} ,... \& Ware, D. (2017). \textit{Improved maize reference genome with single-molecule technologies.} \myuline{Nature} 546(7659), 524–527. \href{https://www.nature.com/articles/nature22971}{DOI}.
    \item \textbf{May, M. R.}, S. Höhna, \& B. R. Moore (2016). \textit{A Bayesian approach for detecting the impact of mass-extinction events on molecular phylogenies when rates of lineage diversification may vary.} \myuline{Methods in Ecology and Evolution} 7(8), 947–959. \href{https://doi.org/10.1111/2041-210X.12563}{DOI}.
    \item Moore, B. R., Höhna, S., \textbf{May, M. R.}, Rannala, B. \& Huelsenbeck, J. P. (2016). \textit{Critically evaluating the theory and performance of Bayesian analysis of macroevolutionary mixtures.} \myuline{Proceedings of the National Academy of Sciences} 34(113), 9569–9574. \href{https://doi.org/10.1073/pnas.1518659113}{DOI}.
    \item \textbf{May, M. R.} \& Moore, B. R. (2016). \textit{How well can we detect lineage-specific diversification-rate shifts? A simulation study of sequential AIC methods.} \myuline{Systematic Biology} 6(65), 1076–1084. \href{https://doi.org/10.1093/sysbio/syw026}{DOI}.
    \item Höhna, S., \textbf{May, M. R.}, \& Moore, B. R. (2016). \textit{TESS: an R package for efficiently simulating phylogenetic trees and performing Bayesian inference of lineage diversification rates.} \myuline{Bioinformatics} 32(5), 789–791. \href{https://doi.org/10.1093/bioinformatics/btv651}{DOI}.
    \item Magee, A. F., \textbf{May, M. R.}, \& Moore, B. R. (2014). \textit{The dawn of open access to phylogenetic data.} \myuline{PLoS One} 9(10), e110268. \href{https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0110268}{DOI}.
    \item Brandvain, Y., Pauly, G. B., \textbf{May, M. R.}, \& Turelli, M. (2014). \textit{Explaining Darwin’s corollary to Haldane’s rule: the role of mitonuclear interactions in asymmetric postzygotic isolation among toads}. \myuline{Genetics} 197(2), 743–747. \href{https://doi.org/10.1534/genetics.113.161133}{DOI}.
    \item Melters, D. P., Bradnam, K. R., Young, H. A., Telis, N., \textbf{May, M. R.}, Ruby, J. G., ... \& Chan, S. W. (2013). \textit{Comparative analysis of tandem repeats from hundreds of species reveals unique insights into centromere evolution.} \myuline{Genome Biology} 14(1), 1–20. \href{https://genomebiology.biomedcentral.com/articles/10.1186/gb-2013-14-1-r10}{DOI}.
    \item \textbf{May, M. R.}, Provance, M. C., Sanders, A. C., Ellstrand, N. C., \& Ross-Ibarra, J. (2009). \textit{A Pleistocene clone of Palmer's oak persisting in southern California.} \myuline{PLoS One} 4(12), e8346. \href{https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0008346}{DOI}.
\end{etaremune}



\subsection*{Presentations}

\begin{etaremune}[topsep=0pt,itemsep=1.2em,partopsep=0pt,parsep=0pt]
    \item \textbf{May, M. R.} \& Rothfels, C. J. (2021). \textit{Mistreating birth-death models as priors in phylogenetic analysis compromises our ability to compare models.} \myuline{Botanical Society of America Conference}. (Invited.)
    \item \textbf{May, M. R.}, Contreras, D. L., Sundue, M. A., Nagalingum, N. S., Looy, C. V., \& Rothfels, C. J. (2021). \textit{Inferring the total-evidence timescale of marattialean fern evolution in the face of model sensitivity.} \myuline{Joint Annual Evolution Meeting}.
    \item \textbf{May, M. R.} \& Moore, B. R. (2017). \textit{A Bayesian method for inferring discrete-state dependent rates of continuous-trait evolution.} \myuline{Joint Annual Evolution Meeting; Portland, Oregon}.
    \item \textbf{May, M. R.}, Moore, B. R., Höhna, S., Huelsenbeck, J. P., \& Rannala, B. (2016). \textit{Towards a correct Bayesian method for inferring lineage-specific rates of speciation and extinction.} \myuline{Joint Annual Evolution Meeting; Austin, Texas}.
    \item \textbf{May, M. R.} (2016). \textit{Problems and solutions for inferring lineage-specific rates of speciation and, extinction.} \myuline{Center for Population Biology seminar series; UC Davis}.
    \item \textbf{May, M. R.} \& Moore, B. R. (2014). \textit{Inferring lineage-specific rates of continuous-trait evolution.} \myuline{Botanical Society of America Conference; Boise, Idaho}.
    \item \textbf{May, M. R.} (2013). \textit{Mostly Bayesian methods for inferring heterogeneous evolutionary processes across phylogenies.} \myuline{Center for Population Biology seminar series; UC Davis}.
    \item \textbf{May, M. R.} \& Moore, B. R., (2013). \textit{Assessing the reliability of MEDUSA using simulation.} \myuline{Joint Annual Evolution Meeting; Snowbird, Utah}.
\end{etaremune}



\subsection*{Fellowships and Awards}

\begin{adjustwidth}{1em}{}
UC Davis Outstanding Graduate Student Teaching Award (2017) \\
NSF GRFP Predoctoral Fellowship (2011--2016)
\end{adjustwidth}

\subsection*{Societies and Services}

\paragraph{Member of:}

\hangindent3em
\textit{Society of Systematic Biologist}, \textit{Society for the Study of Evolution}, \textit{Botanical Society of America}.

\paragraph{Peer Review for:}

\hangindent3em
\textit{Systematic Biology}, \textit{Proceedings of the National Academy of Sciences}, \textit{Proceedings of the Royal Society B}, \textit{Methods in Ecology and Evolution}, \textit{Frontiers in Plant Science}, \textit{Functional Ecology}, \textit{Molecular Biology and Evolution}, \textit{PLoS One}, \textit{PeerJ}.

% \subsection*{Mentorship}

\subsection*{Teaching}

\begin{tabularx}{\textwidth}{@{\hspace{1em}}lX}
    2021 & Instructor for Stay-At-Home RevBayes Workshop.\\
    2019 & Instructor for Madrid Phylogenetics Workshop.\\
    2019 & Organizer and instructor for Bodega Applied Phylogenetics Workshop.\\
    2018 & Instructor for Madrid Phylogenetics Workshop.\\
    2018 & Teaching assistant for EVE 103: Phylogeny and Macroevolution (UC Davis).\\
    2017 & Organizer and instructor for Bodega Applied Phylogenetics Workshop.\\
    2016 & Teaching assistant for EVE 103: Phylogeny and Macroevolution (UC Davis). (Awarded UC Davis Outstanding Graduate Student Teaching Award 2017)\\
    2015 & Organizer and teaching assistant for Bodega Applied Phylogenetics Workshop.\\
    2014 & Organizer and teaching assistant for Bodega Applied Phylogenetics Workshop.\\
    2013 & Organizer and teaching assistant for Bodega Applied Phylogenetics Workshop.\\
    2012 & Teaching assistant for EVE 103: Phylogeny and Macroevolution (UC Davis).
\end{tabularx}


\subsection*{Software Tutorials}

\begin{etaremune}[topsep=0pt,itemsep=1.2em,partopsep=0pt,parsep=0pt]
    \item \textbf{May, M. R.} \& Höhna, S. \textit{Rev Language Syntax: A very short introduction to the Rev language.} \href{https://revbayes.github.io/tutorials/intro/rev.html}{Link}.
    \item Tribble, C. M. \& \textbf{May, M. R.} \textit{Introduction to RevGadgets: Plotting the output of RevBayes analyses in the R package RevGadgets.} \href{https://revbayes.github.io/tutorials/intro/revgadgets.html}{Link}.
    \item \textbf{May, M. R.}, Moore, B. R., \& Höhna, S. \textit{Introduction to MCMC using RevBayes: Introduction to MCMC simulation using a simple binomial model.} \href{https://revbayes.github.io/tutorials/mcmc/binomial.html}{Link}.
    \item \textbf{May, M. R.} \& Höhna, S. \textit{Model Selection of Partition Models: Comparing relative model fit with Bayes factors.} \href{https://revbayes.github.io/tutorials/model_selection_bayes_factors/bf_partition_model.html}{Link}.
    \item \textbf{May, M. R.} \& Höhna, S. \textit{Model Averaging of Substitution Models: Reversible-jump MCMC over substitution models.} \href{https://revbayes.github.io/tutorials/model_selection_bayes_factors/bf_subst_model_rj.html}{Link}.
    \item Höhna, S. \& \textbf{May, M. R.} \textit{Branch-Specific Diversification Rate Estimation: How to estimate branch-specific shifts in diversification rates.} \href{https://revbayes.github.io/tutorials/divrate/branch_specific.html}{Link}.
    \item Höhna, S., Freyman, W. A., \& \textbf{May, M. R.} \textit{Diversification Rate Estimation with Missing Taxa: How to estimate diversification rates with incomplete taxon sampling.} \href{https://revbayes.github.io/tutorials/divrate/sampling.html}{Link}
    \item \textbf{May, M. R.} \textit{Simple Brownian Rate Estimation: Estimating rates of Brownian-motion evolution.} \href{https://revbayes.github.io/tutorials/cont_traits/simple_bm.html}{Link}.
    \item \textbf{May, M. R.} \textit{Relaxed Brownian Rate Estimation: Estimating branch-specific rates of Brownian-motion evolution.} \href{https://revbayes.github.io/tutorials/cont_traits/relaxed_bm.html}{Link}.
    \item \textbf{May, M. R.} \textit{State-Dependent Brownian Rate Estimation: Estimating state-dependent rates of Brownian-motion evolution.} \href{https://revbayes.github.io/tutorials/cont_traits/state_dependent_bm.html}{Link}.
    \item \textbf{May, M. R.} \textit{Multivariate Brownian Motion: Accounting for correlations among continuous traits.} \href{https://revbayes.github.io/tutorials/cont_traits/multivariate_bm.html}{Link}.
    \item \textbf{May, M. R.} \textit{Simple Ornstein-Uhlenbeck Models: Estimating optima under Ornstein-Uhlenbeck evolution.} \href{https://revbayes.github.io/tutorials/cont_traits/simple_ou.html}{Link}.
    \item \textbf{May, M. R.} \textit{Relaxed Ornstein-Uhlenbeck Models: Estimating lineage-specific optima under Ornstein-Uhlenbeck evolution.} \href{https://revbayes.github.io/tutorials/cont_traits/relaxed_ou.html}{Link}.
\end{etaremune}